---
title: "Homework 1"
author: "Iris (Ziyi) Wang"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
```

##Problem 1
Create a data frame comprised of:
- a random sample of size 10 from a standard Normal distribution
- a logical vector indicating whether elements of the sample are greater than 0
- a character vector of length 10
- a factor vector of length 10, with 3 different factor “levels”

```{r create_df}
prob1_df =
    tibble(
        samp = rnorm(10),
        samp_gt_0 = samp > 0,
        char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
        factor_vec = c("low", "low", "low", "mod", "mod", "mod","mod", "high", "high", "high")
    )
```

Take the mean of each variable in my data frame.

```{r mean_pull_var}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))
```

I can take the mean of numbers and logical but not character or factor. 

```{r try_numeric}
as.numeric(pull(prob1_df, samp))
as.numeric(pull(prob1_df, samp_gt_0))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))
```
I can convert logical variable to numeric variable, but I cannot convert character and factor variables to numeric variables. So this does explain the reason why I get the error messages when I was trying to take the mean of character and factor variables while it is fine to take the mean of my numeric and logical variables.

```{r}
# convert the logical vector to numeric, and multiply the random sample by the result
as.numeric(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)

# convert the logical vector to a factor, and multiply the random sample by the result
as.factor(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)

# convert the logical vector to a factor and then convert the result to numeric, and multiply the random sample by the result
as.numeric(as.factor(pull(prob1_df, samp_gt_0))) * pull(prob1_df, samp)
```

## Problem 2
```{r}
#install.packages("palmerpenguins")
data("penguins", package = "palmerpenguins")
```

- Write a short description of the penguins dataset using inline R code, including:
1. the data in this dataset, including names / values of important variables
```{r}
summary(penguins)
```

2. the size of the dataset is  `r nrow(penguins)` (rows) by `r ncol(penguins)` (columns).

3. the mean flipper length is `r mean(pull(penguins, flipper_length_mm), na.rm=T)`mm.

- Make a scatterplot of flipper_length_mm (y) vs bill_length_mm (x); color points using the species variable (adding color = ... inside of aes in your ggplot code should help).
```{r}
ggplot(penguins, 
       aes(x = bill_length_mm, 
           y = flipper_length_mm, 
           color = species)) + geom_point() + ggtitle("Scatterplot")
```

- Export your first scatterplot to your project directory using ggsave.
```{r}
ggsave("Scatterplot.pdf", height = 5, width = 5)
```